Increasing the mortality gap? Social inequality in mortality among elderly and adults in Northern Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}

### 2017-10-24 cape.Rnw
fix small errors

\begin{itemize}
\item Development over \emp{time}.
  \begin{itemize}
\item Explicit or implicit assumption of an \epm{eternal} social gradient in history in many theories (Omran, Link and Phelan, Marmot, McKeown), some implying even larger in history.
\item Antonovsky – divergence followed by convergence
\end{itemize}
\item Development over the \emp/life course}
  \begin{itemize}
\item Convergence, divergence or maintenance.
\item Antonovsky – large differences in adulthood, convergence in old age
\end{itemize}

@@

Thank you for your attention!

\end{center}

>>>>

\begin{itemize}
\item Development over \emp{time}.
  \begin{itemize}
\item Explicit or implicit assumption of an \emp{eternal} social gradient in history in many theories (Omran, Link and Phelan, Marmot, McKeown), some implying even larger in history.
\item Antonovsky – divergence followed by convergence
\end{itemize}
\item Development over the \emp{life course}
  \begin{itemize}
\item Convergence, divergence or maintenance.
\item Antonovsky – large differences in adulthood, convergence in old age
\end{itemize}
\end{itemize}

@@

\vspace{1\baselineskip}
\textcolor{red}{\fbox{Thank you for your attention!}}

\includegraphics[height=5cm]{myfigs/Top_incomes}
\end{center}
